Data Preparation

### 2019-01-09 Data Preparation.Rmd
test

---
title: "Data Preparation"
author: "DARS"
date: "1/9/2019"
output: pdf_document
---
# Libraries:
```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
```

@@

# Variable Engineering

>>>>

---
title: "Data Preparation"
author: "DARS"
date: "1/9/2019"
output: pdf_document
---
#Libraries:
```{r setup, include=FALSE}

library(tidyverse)
library(tidytext)

library(tm          ) # text mining
library(topicmodels)  #topic modeling

library(pdftools)
library(ggplot2)

```

@@

# Variable Engineering
We create a dataframe from the Corpus:
```{r}

manuals_td <- tidy(corpus_manuals)

```
#TEST
```{r}
test <- "test" 
```
